SoK: Web Application Attack Defenses (in Question)

### 2014-10-09 docs/questioning.tex
correction
new subcategory and entry

@@

	\multirow{9}{*}{Runtime Tainting}

@@

	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (15,{\sc nq},{\sc nq},{\sc nq})\_r & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\

@@

@@

        \multirow{11}{*}{Training}

>>>>

% {\sc html} injection --- such attacks pose no threat to cookies and session IDs.

@@

	\multirow{8}{*}{Runtime Tainting}

@@

	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\

@@

  \multirow{3}{*}{Parse-Tree Validation}
  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\

@@

        \multirow{10}{*}{Training}
